### 2013-11-22 research/paper/figure/coefficient-table.tex
applied kenny's changes
Committing small changes to th mathematical model and some initial changes to the results section

\caption{Coefficient values used in the 7th order interpolation polynomial for high ($Re=22300$) and low ($Re=165$) Reynolds numbers. These data are used as input data to calculate the RHS of Eq.\ref{final_equation_motion} throughout this study.}

\label{table:nonlin} % is used to refer this table in the text
\end{center}
\end{table}

>>>>

\caption{Coefficient values used in the 7th order interpolation polynomial for high ($Re=22300$) and low ($Re=165$) Reynolds numbers. These data are used as input data to calculate the right-hand side of Eq. \ref{final_equation_motion} throughout this study.}

\label{table:cy-coefficients} % is used to refer this table in the text
\end{center}
\end{table}

### 2013-11-22 research/paper/results/results-2.3.tex
Committing comments on abstract and introduction.
Committing mathematical_model.tex
Committing small changes to th mathematical model and some initial changes to the results section

 \section{Results}

@@

The stationary the force characteristic data ($C_y$) as a function of incident angle obtained using flow simulations (Fig.\ref{cy ploynomial}(a)) have a good agreement with data presented in \cite{Joly2012}. In comparison with the 7th order polynomial curve at \reynoldsnumber=22300 (Fig.\ref{cy ploynomial}(b)),  several differences could be observed. The peak value of $C_y$ is  significantly low at \reynoldsnumber=165 ($C_y=0.05$ at $4^0$) in comparison with \reynoldsnumber=22300 ($C_y=0.57$ at $13^0$) . The inflection point present at \reynoldsnumber=22300 could not be observed at \reynoldsnumber=165. This agrees with the findings of \cite{Luo2003}. It was concluded by \cite{Luo2003} that hysteresis occur due to the inflection point found in the $C_y$ curve. Therefore hysteresis is not expected at \reynoldsnumber=165. The range of the incident flow angles where $C_y$ remain positive is narrow at \reynoldsnumber=165 ($0^0 <\theta \leq$ $6^0$) compared to \reynoldsnumber=22300 ($0^0 <\theta \leq 15^0$). This feature is what sustains galloping and power is transferred from the fluid to the supporting structure within this range of incident angles because fluid forces are acting in the direction of travel of the oscillating cylinder. Incident angles beyond this range actually suppresses the galloping and power goes in the opposite direction. Therefore due to the overall smaller $C_y$ and narrow range of angles where $C_y$ is positive for \reynoldsnumber=165 compared to \reynoldsnumber=22300, it is expected that power output at \reynoldsnumber=165 is significantly lower than at \reynoldsnumber=22300.

@@

 Power could be expressed as the product of force and velocity. Therefore the transferred power form fluid-to-body could be expressed as $P_t=F_y\dot{y}$. Similarly the dissipated power due to the mechanical damping could be expressed as $P_d=(c\dot{y})\dot{y}$. The time average of these two quantities should be equal due to energy conservation, provided that the mechanical friction is neglected . Analysing the  time histories of $P_t $ and $P_d$ at key regions (Fig.\ref{fig:regions_1}) on the mean power vs $U^*$ provides a detailed explanation for the variation of the output power when the reduced velocity is increased. The key regions consists of region 1 where the $P_{mean}$ increases with \ustar, region 2 where $P_{mean}$ becomes maximum and region 3 where $P_{mean}$ decreases with \ustar. It has been established earlier that the damping factor is a function of $U^*$. Therefore it could be derived that $U^*$ is inversely proportional to damping coefficient. Hence the damping coefficient reduces when you move from region 1 to 3. Fig \ref{fig:lift_curves} (a) shows that $C_y$ and therefore instantaneous force rises until $4^0$ where it peaks and then falls and at around $6^0$ becomes negative. The maximum amount of power that could be transferred occurs near the peak region. At the region where the instantaneous force becomes negative it will be opposing the velocity $\dot{y}$. Data at $\zeta=0.1$, $m^*=40$ and \reynoldsnumber=165 (Fig.\ref{fig:power_time_histories}) are analysed as and example.

@@

 At region 1 where $U^*=90$ the damping constant is high and a clear sinusoidal signal could be observed for both $P_d$ and $P_t$ in Fig.\ref{fig:power_time_histories} (a). Fig.\ref{fig:power_time_histories} (d) and (g) shows that $\theta$ is in line or in phase with $F_y$.  The velocity amplitude in this case is small and the equivalent incident angle within the range where the hydrodynamic force increases with the incident angle (i.e. $0<\theta \leq 4^0$ in Fig.\ref{fig:lift_curves} (a)) Hence both $P_d$ and $P_t$ becomes sinusoidal. In this case, power output is limited by the low fluid forces present at low incident angles. In other words damping is significantly high and extracts a lot of power that the velocity amplitude could not grow where the forcing  is significant to produce high level of power.

  At region 3 ($U^*= 400$) `$c$' is low in comparison with region 1 and 2 which leads to a low mean power output. Fig.\ref{fig:power_time_histories} (c) shows that $P_t$ becomes negative over some portion of the cycle. This is caused by te high velocity amplitude leads to the equivalent incident angle $\theta$, in this case to exceed the range where $C_y$ is positive (i.e. $0<\theta<6^0$ in Fig.\ref{cy ploynomial} (a)). In this portion of the cycle the hydrodynamic force actually opposes the direction of travel and power is transferred from the structure to the fluid during those times. From and energy perspective, the mechanical damping is not sufficient to remover the energy transferred from the fluid to the structure during other times of the cycle because $\frac{c}{\rho\mathcal{A}U}$ is substantially low. Therefore this excess energy is transferred back to the fluid as depicted by the negative region of $P_d$ in Fig.\ref{fig:power_time_histories} (c)

At region 2 ($U^*=165$). $P_t$ is not a pure sinusoidal signal. However, the  signal remains periodic. From the time history graph of $P_t$, two `peaks' are present in a single half cycle (Fig \ref{fig:power_time_histories} (b)). In this case, the velocity amplitude actually exceeds the equivalent incident angle where the hydrodynamic forces peaks (i.e. $\theta=4^0$ in \ref{cy ploynomial} (a)). The dips in $P_d$ between the two peaks approximately correspond to the time where the transverse velocity is higher than 0.07 and $F_y$ is decreasing with increasing transverse velocity. The mean power output is at its maximum. This is due to the fact that this region is a best compromise between region 1 and 3. The damping is substantially high to obtain a high power output while not too high to allow the induced angle of attack to enter the region where the forcing opposes the direction of travel.

@@

\section{Conclusion}

>>>>

\section{Results}
\label{sec:results}

@@

The characteristic lift force data for a stationary body ($C_y$) as a function of incident angle $\theta$ obtained using flow simulations are shown in figure \ref{cy ploynomial}(a). They agree well with the low \reynoldsnumber\ data presented in \citet{Joly2012}.

However, there are several differences that can be observed when the low \reynoldsnumber\ data are compared with the $7^{th}$ order polynomial curve at $\reynoldsnumber=22300$ shown in figure \ref{cy ploynomial}(b). The peak value of $C_y$ is  significantly lower at $\reynoldsnumber=165$ ($C_y=0.05$ at $4^\circ$) in comparison with $\reynoldsnumber=22300$ ($C_y=0.57$ at $13^\circ$) . The inflection point present around $8^\circ$ for $\reynoldsnumber=22300$ is not observed at $\reynoldsnumber=165$. This agrees with the findings of \cite{Luo2003}.

It was concluded by \cite{Luo2003} that hysteresis in the system response occurs due to the inflection point in the $C_y$ curve. Therefore hysteresis is not expected at $\reynoldsnumber=165$.

The range of incident flow angles where $C_y$ remains positive is narrow at $\reynoldsnumber=165$ ($0^\circ <\theta \leq$ $6^\circ$) compared to $\reynoldsnumber=22300$ ($0^\circ <\theta \leq 15^\circ$). This feature is what sustains galloping. Power is only transferred from the fluid to the supporting structure within this range of incident angles because fluid forces are acting in the direction of travel of the oscillating cylinder, as demonstrated by equation \ref{power_alt}. Incident angles beyond this range actually suppress the galloping and power goes in the opposite direction, i.e; form body to fluid. Therefore due to the overall smaller $C_y$ and narrow range of angles where $C_y$ is positive for $\reynoldsnumber=165$ compared to $\reynoldsnumber=22300$, it is expected that power output at $\reynoldsnumber=165$ is significantly lower than at $\reynoldsnumber=22300$.

@@

 Power could be expressed as the product of force and velocity. Therefore the transferred power form fluid-to-body could be expressed as $P_t=F_y\dot{y}$. Similarly the dissipated power due to the mechanical damping could be expressed as $P_d=(c\dot{y})\dot{y}$. The time average of these two quantities should be equal due to energy conservation, provided that the mechanical friction is neglected . Analysing the  time histories of $P_t $ and $P_d$ at key regions (Fig.\ref{fig:regions_1}) on the mean power vs $U^*$ provides a detailed explanation for the variation of the output power when the reduced velocity is increased. The key regions consists of region 1 where the $P_{mean}$ increases with \ustar, region 2 where $P_{mean}$ becomes maximum and region 3 where $P_{mean}$ decreases with \ustar. It has been established earlier that the damping factor is a function of $U^*$. Therefore it could be derived that $U^*$ is inversely proportional to damping coefficient. Hence the damping coefficient reduces when you move from region 1 to 3. Fig \ref{fig:lift_curves} (a) shows that $C_y$ and therefore instantaneous force rises until $4^\circ$ where it peaks and then falls and at around $6^\circ$ becomes negative. The maximum amount of power that could be transferred occurs near the peak region. At the region where the instantaneous force becomes negative it will be opposing the velocity $\dot{y}$. Data at $\zeta=0.1$, $m^*=40$ and \reynoldsnumber=165 (Fig.\ref{fig:power_time_histories}) are analysed as and example.

@@

 At region 1 where $U^*=90$ the damping constant is high and a clear sinusoidal signal could be observed for both $P_d$ and $P_t$ in Fig.\ref{fig:power_time_histories} (a). Fig.\ref{fig:power_time_histories} (d) and (g) shows that $\theta$ is in line or in phase with $F_y$.  The velocity amplitude in this case is small and the equivalent incident angle within the range where the hydrodynamic force increases with the incident angle (i.e. $0<\theta \leq 4^\circ$ in Fig.\ref{fig:lift_curves} (a)) Hence both $P_d$ and $P_t$ becomes sinusoidal. In this case, power output is limited by the low fluid forces present at low incident angles. In other words damping is significantly high and extracts a lot of power that the velocity amplitude could not grow where the forcing  is significant to produce high level of power.

  At region 3 ($U^*= 400$) `$c$' is low in comparison with region 1 and 2 which leads to a low mean power output. Fig.\ref{fig:power_time_histories} (c) shows that $P_t$ becomes negative over some portion of the cycle. This is caused by te high velocity amplitude leads to the equivalent incident angle $\theta$, in this case to exceed the range where $C_y$ is positive (i.e. $0<\theta<6^\circ$ in Fig.\ref{cy ploynomial} (a)). In this portion of the cycle the hydrodynamic force actually opposes the direction of travel and power is transferred from the structure to the fluid during those times. From and energy perspective, the mechanical damping is not sufficient to remover the energy transferred from the fluid to the structure during other times of the cycle because $\frac{c}{\rho\mathcal{A}U}$ is substantially low. Therefore this excess energy is transferred back to the fluid as depicted by the negative region of $P_d$ in Fig.\ref{fig:power_time_histories} (c)

At region 2 ($U^*=165$). $P_t$ is not a pure sinusoidal signal. However, the  signal remains periodic. From the time history graph of $P_t$, two `peaks' are present in a single half cycle (Fig \ref{fig:power_time_histories} (b)). In this case, the velocity amplitude actually exceeds the equivalent incident angle where the hydrodynamic forces peaks (i.e. $\theta=4^\circ$ in \ref{cy ploynomial} (a)). The dips in $P_d$ between the two peaks approximately correspond to the time where the transverse velocity is higher than 0.07 and $F_y$ is decreasing with increasing transverse velocity. The mean power output is at its maximum. This is due to the fact that this region is a best compromise between region 1 and 3. The damping is substantially high to obtain a high power output while not too high to allow the induced angle of attack to enter the region where the forcing opposes the direction of travel.

@@

\section{Conclusion}
\label{sec:conc}
